The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2014-01-24 papers/pair-correlation/paper.tex
respond to Paho questions about figures Tested on bennet. Took 5:08.12.

\begin{figure*}
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-1.pdf}
    \vspace{-0.6cm}
    \caption{Pair distribution function near a hard wall with $\eta = 0.1$.}
    \label{fig:pair-distribution-1}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-3.pdf}
    \vspace{-0.6cm}
    \caption{Pair distribution function near a hard wall with $\eta = 0.3$.}
    \label{fig:pair-distribution-3}
  \end{subfigure}
  \caption{ \paircaption \fixme{Do we want to label the y-axis for the 1d plots?}
  }\label{fig:pair-distribution}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Tweak spacing, add a, b, c, etc. The 1d plots still have two curves for this work, do we want to remove one?} The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution-3}
\end{figure*}
% \begin{figure}
%   \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-contact-4.pdf}
%   \caption{The triplet distribution function
%     $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.4, plotted when
%     $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
%     shows the triplet distribution function, with white corresponding
%     to the contact value of the \emph{pair} distribution function.
%     The plot on the right shows the value of $g^{(3)}$ along the path
%     shown as a dotted line on the plot to the
%     left.}\label{fig:triplet-contact-distribution-4}
% \end{figure}

@@

\begin{figure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-3-2.pdf}
    \vspace{-0.8cm}
    \caption{Sticky hard-sphere fluid}\label{fig:dadz-delta}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-square-well-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core square well fluid}\label{fig:dadz-square-well}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-inverse-sixth-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core inverse-sixth fluid}\label{fig:dadz-inverse-sixth}
  \end{subfigure}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard
    wall.\fixme{Do we want y-axis ticks or no? Also, why does the data start
      at $z = 0$?}}
  \label{fig:dadz}
\end{figure}

>>>>

\begin{figure*}
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-1.pdf}
    \vspace{-0.6cm}
    \caption{Pair distribution function near a hard wall with $\eta = 0.1$.}
    \label{fig:pair-distribution-1}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
    \includegraphics[width=\linewidth]{figs/pair-correlation-pretty-3.pdf}
    \vspace{-0.6cm}
    \caption{Pair distribution function near a hard wall with $\eta = 0.3$.}
    \label{fig:pair-distribution-3}
  \end{subfigure}
  \caption{ \paircaption \fixme{Do we want to label the y-axis for the
      1d plots? } \davidsays{I think so...}
  }\label{fig:pair-distribution}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-contact-3.pdf}\\
  \includegraphics[width=\textwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{\fixme{Tweak spacing, add a, b, c, etc. The 1d plots still
      have two curves for this work, do we want to remove one?
      \davidsays{I'm not sure, I might be tempted to keep both,
        although if we do we should explain the difference between
        them. (left-right mirror image)}} The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted line on the plot to the
    left.}\label{fig:triplet-contact-distribution-3}
\end{figure*}
% \begin{figure}
%   \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-contact-4.pdf}
%   \caption{The triplet distribution function
%     $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.4, plotted when
%     $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
%     shows the triplet distribution function, with white corresponding
%     to the contact value of the \emph{pair} distribution function.
%     The plot on the right shows the value of $g^{(3)}$ along the path
%     shown as a dotted line on the plot to the
%     left.}\label{fig:triplet-contact-distribution-4}
% \end{figure}

@@

\begin{figure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-3-2.pdf}
    \vspace{-0.8cm}
    \caption{Sticky hard-sphere fluid}\label{fig:dadz-delta}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-square-well-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core square well fluid}\label{fig:dadz-square-well}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-inverse-sixth-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core inverse-sixth fluid}\label{fig:dadz-inverse-sixth}
  \end{subfigure}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard wall.\fixme{Do we
      want y-axis ticks or no? Also, why does the data start at $z =
      0$? \davidsays{I think ticks on the vertical axis aren't needed
        because we are not including the scale (which depends on
        prefactors).  I think data starting at $z=0$ is a result of a
        (poor?) choice of where to define $z=0$.  It's the same
        definition we use in Fig. 2, so I think the two should stay
        consistent...}}}
  \label{fig:dadz}
\end{figure}
